R Python, and Ruby clients for GBIF species occurrence data

### 2017-09-26 manuscript.Rmd
update manuscript with correct doi

All scripts and data used in this paper can be found in the permanent
data archive Zenodo under the digital object identifier
(<https://doi.org/10.5281/zenodo.997547>). This DOI
corresponds to a snapshot of the GitHub repository at
<https://github.com/sckott/gbifms> that matches this preprint. Software
can be found at <https://github.com/ropensci/rgbif>, <https://github.com/sckott/pygbif>,
and <https://github.com/sckott/gibfrb>, all under MIT licenses. We thank
all the users that have used `rgbif`, `pygbif`, and `gbifrb` and have
given feedback and reported bugs. In addition, we greatly appreciate
all the contributors to the three libraries, found at
<https://github.com/ropensci/rgbif/graphs/contributors>,
<https://github.com/sckott/pygbif/graphs/contributors>, and
<https://github.com/sckott/gbifrb/graphs/contributors>.

>>>>

All scripts and data used in this paper can be found in the permanent
data archive Zenodo under the digital object identifier
(<https://doi.org/10.5281/zenodo.997554>). This DOI
corresponds to a snapshot of the GitHub repository at
<https://github.com/sckott/gbifms> that matches this preprint. Software
can be found at <https://github.com/ropensci/rgbif>, <https://github.com/sckott/pygbif>,
and <https://github.com/sckott/gibfrb>, all under MIT licenses. We thank
all the users that have used `rgbif`, `pygbif`, and `gbifrb` and have
given feedback and reported bugs. In addition, we greatly appreciate
all the contributors to the three libraries, found at
<https://github.com/ropensci/rgbif/graphs/contributors>,
<https://github.com/sckott/pygbif/graphs/contributors>, and
<https://github.com/sckott/gbifrb/graphs/contributors>.

### 2017-09-26 manuscript.tex
update manuscript with correct doi

All scripts and data used in this paper can be found in the permanent
data archive Zenodo under the digital object identifier
(\url{https://doi.org/10.5281/zenodo.997547}). This DOI corresponds to a
snapshot of the GitHub repository at
\url{https://github.com/sckott/gbifms} that matches this preprint.
Software can be found at \url{https://github.com/ropensci/rgbif},
\url{https://github.com/sckott/pygbif}, and
\url{https://github.com/sckott/gibfrb}, all under MIT licenses. We thank
all the users that have used \texttt{rgbif}, \texttt{pygbif}, and
\texttt{gbifrb} and have given feedback and reported bugs. In addition,
we greatly appreciate all the contributors to the three libraries, found
at \url{https://github.com/ropensci/rgbif/graphs/contributors},
\url{https://github.com/sckott/pygbif/graphs/contributors}, and
\url{https://github.com/sckott/gbifrb/graphs/contributors}.

>>>>

All scripts and data used in this paper can be found in the permanent
data archive Zenodo under the digital object identifier
(\url{https://doi.org/10.5281/zenodo.997554}). This DOI corresponds to a
snapshot of the GitHub repository at
\url{https://github.com/sckott/gbifms} that matches this preprint.
Software can be found at \url{https://github.com/ropensci/rgbif},
\url{https://github.com/sckott/pygbif}, and
\url{https://github.com/sckott/gibfrb}, all under MIT licenses. We thank
all the users that have used \texttt{rgbif}, \texttt{pygbif}, and
\texttt{gbifrb} and have given feedback and reported bugs. In addition,
we greatly appreciate all the contributors to the three libraries, found
at \url{https://github.com/ropensci/rgbif/graphs/contributors},
\url{https://github.com/sckott/pygbif/graphs/contributors}, and
\url{https://github.com/sckott/gbifrb/graphs/contributors}.
